---
title: "Midterm_Interactive Dashboard"
author: "Zhongyuan Zhang"
date: "6/11/2020"
output: html_document
---

```{r}
library(shiny)
library(plotly)
```

## Dashboard Project

Build an interactive visualization using the data sets quiz-categories.csv and midterm-results.csv. These data represent midterm results from an open book test. The categories represent the skills required to answer each question:

wrangling - Question required data manipulations skills  
coding - Question required coding skills  
d.trees - Question invoilved decision trees  
sna - Question involved social network analysis  
nlp - Question involved natural language processing  
viz - Question involved visualization of data  
n.nets - Question involved neural nets  
googleable - Question could be answered by searching the internet  
non-googleable - Question could not be answered through simple searching of the internet  
jitl - Question involved learning somethimg new (just in time learning)  
substantive - Question involved wrestling with a complex idea that does not have a definitive answer

```{r}
quiz<-read.csv("quiz-categories.csv",stringsAsFactors = FALSE,header = TRUE)
```

```{r}
midterm<-read.csv("midterm-results.csv",stringsAsFactors = FALSE,header = TRUE)
```

## About the quiz question items
## Want to look at content validity by viewing what topic(s) each item is tested and their frequency.
## Calculate the item difficulty using classical testing theory
```{r}
library(tidyverse)
#transforming wide data into long data
quiz_reshape<-gather(quiz,categories,cover,-Question)

#removing necessary strings
quiz_reshape$Question<-gsub("Q","",quiz_reshape$Question)
quiz_reshape$Question<-gsub("_c","",quiz_reshape$Question)
quiz_reshape$Question<-as.numeric(quiz_reshape$Question)


quiz_reshape$Question<-factor(quiz_reshape$Question)

#filter for topic involved only, 0 values were removed
quiz_reshape1<-filter(quiz_reshape,cover!=0)
```


```{r}
library(RColorBrewer)
par(mar=c(3,4,2,2))
display.brewer.all()
library(colorRamps)

# Define the number of colors you want
nb.cols <- length(unique(quiz_reshape1$categories))
mycolors <- colorRampPalette(brewer.pal(9, "GnBu"))(nb.cols)

#Topics each question item covers
ggplot(quiz_reshape1,aes(x=Question,fill=categories))+
  geom_bar()+
  coord_flip()+ylim(c(0,5))+
  ylab("Topics each question item covers")+
  xlab("Question Item")+
  theme(rect=element_blank(),
        line=element_blank())+
  scale_fill_manual(values = mycolors)

# frequency of topics covered
ggplot(quiz_reshape1,aes(x=categories,fill=categories))+
  geom_bar()+ylim(c(0,25))+
  theme(rect=element_blank(),
        line=element_blank())+
  theme(axis.text.x  = element_text(angle=45, hjust = 1))+
  xlab("Distribution of Categories covered in the Quiz")+
  scale_fill_manual(values = mycolors)

#item difficulty; using classical item theories
item_diff<-data.frame(colMeans(midterm[,c(3:32)]))
item_diff$id<-1:dim(item_diff)[1]
item_diff$id<-factor(item_diff$id)
names(item_diff)<-c("item_difficulty_rate","Question")

item_diff<-item_diff%>%
  mutate(item_difficulty=case_when(item_difficulty_rate<=0.33 ~"Difficult",
                                    item_difficulty_rate<=0.66 ~"Medium",
                                   item_difficulty_rate<=1 ~"Easy"
                                               ))


ggplot(item_diff,aes(x=Question,y=item_difficulty_rate))+
  geom_line(group=1)+
  geom_point(aes(col=item_difficulty))+
  theme(rect=element_blank(),
        line=element_blank())+
  labs(title = "Distribution of Question items with Different Difficulty")
  
```

## About the clickcount and time spent on each item
## Display each individual's mastery of the tpoics

```{r}
#How each of the student master the topics 
midterm_long<-midterm[,c(1,3:32)]
names(midterm_long)<-c('id',1:30)
midterm_long<-gather(midterm_long,Question,Outcome,-id)
midterm_long<-left_join(midterm_long,quiz_reshape1,by="Question")
midterm_long$Outcome<-factor(midterm_long$Outcome,labels = c("Wrong","Correct"))

test<-subset(midterm_long,id==1962)

#plot of individual's mastery of each categeory(criteria: Correct rate )
ggplot(test,aes(x=categories,fill=Outcome))+
  geom_bar(position = "fill",width = 0.6)+
  theme(rect=element_blank(),
        line=element_blank(),
        )+
  #adjusting the x-axis labels
  theme(axis.text.x  = element_text(angle=45, hjust = 1))+
  xlab("Categories")+
  ylab("Proportion of Correct Answers")
```

## Display each individual's time(in a chronical order) and clickcount
```{r}
#Total score , correct rate and percentile(for rendertable: results)
midterm$totalscore<-rowSums(midterm[,3:32]) 
midterm$correctrate<-rowMeans(midterm[,3:32])
midterm$percentile<-percent_rank(rowSums(midterm[,3:32]))

#How much time each student spends on the each question item
midterm_items<-midterm[,c(1,33:88)]
even<-seq(2,57,by=2)#select the even colume
midterm_items_time<-midterm_items[,even]
names(midterm_items_time)<-c(1:7,8.9,10,11,12.13,14:30)
midterm_items_time<-cbind(midterm_items[,1:2],midterm_items_time) 
midterm_items_time<-midterm_items_time[,c(1,3:30)]#change the name, to ensure all the colnames gathered are in same type

midterm_items_time_long<-gather(midterm_items_time,Question,Time,-id)
midterm_items_time_long$Question<-factor(midterm_items_time_long$Question,c(1:7,8.9,10,11,12.13,14:30))

#To highlight
#Since in the clickcount and timing part, several items were combined together;here we reshape the data and adjust the sequence of the column
correct<-midterm[,c(1,3:32)]
correct$'8.9'<-correct$Q8_c+correct$Q9_c
correct$`8.9`<-ifelse(correct$`8.9`==2,1,0)

correct$'12.13'<-correct$Q12_c+correct$Q13_c
correct$`12.13`<-ifelse(correct$`12.13`==2,1,0)

#adjust sequence
correct<-correct[,-c(9,10,13,14)]
correct<-correct[,c(1:8,28,9:10,29,11:27)]
names(correct)<-c('id',1:7,8.9,10,11,12.13,14:30)

#from wide to long
correct<-gather(correct,Question,Outcome,-id)
correct$Question<-factor(correct$Question,c(1:7,8.9,10,11,12.13,14:30))
correct$Outcome<-factor(correct$Outcome,labels = c("Wrong","Correct"))

#left_join base on two column, to add the correct feature to the graph
a<-left_join(midterm_items_time_long,correct,by=c("id","Question"))

#single example
test1<-subset(a,id==1170)

#plot of individual's mastery of each categeory(criteria: Correct rate )
p1<-ggplot(test1,aes(x=Question,y=Time))+
  geom_point(aes(col=Outcome))+geom_line(group = 1)+
  theme(rect=element_blank()
  )+
  ylim(c(0,800))

#How many times the student has clicked for each question item,clickcount
midterm_items_clickcount<-midterm_items[,-even]
names(midterm_items_clickcount)<-c('id',1:7,8.9,10,11,12.13,14:30)
midterm_items_clickcount<-gather(midterm_items_clickcount,Question,Click,-id)
midterm_items_clickcount$Question<-factor(midterm_items_clickcount$Question,c(1:7,8.9,10,11,12.13,14:30))

#left_join base on two column, to add the correct feature to the graph
a1<-left_join(midterm_items_clickcount,correct,by=c("id","Question"))
#single example
test2<-subset(a1,id==1170)  

#plot of individual's mastery of each categeory(criteria: Correct rate )
p2<-ggplot(test2,aes(x=Question,y=Click))+
  geom_col(aes(fill=Outcome))+
  theme(rect=element_blank()
  )

#align two plots together
#Stacking multiple plots vertically with the same X axis but different Y axes
library(grid)
grid.newpage()
grid.draw(rbind(ggplotGrob(p1), ggplotGrob(p2), size ="last") )   

```
## Expolore relationship btw click count, time in general 
```{r}
#create a table where all the information are included for the interactive plot
relation<-left_join(a,a1,by=c("id","Question"))
relation<-relation[,-c(2,4)]
head(relation)

ggplot(relation, aes(x=Time,y=Click,col=Outcome.y,size=Click))+
  geom_point()+
  theme(rect=element_blank())
  
```



```{r}
ui <- fluidPage(
  h1("Midterm Results Dashboard"),
  sidebarLayout(
  sidebarPanel("Welcome! Congrats! It's been half of the semster, let's check how well you are doing so far.
               Don't worry if you find the result least satisfactory. It's only a diagonisc report with 
               possible measurement error. Take it as a stepping stone for your next progress. Good luck!",
              
               selectInput("studentid",label="Please select your id to see your quiz
                           results and corresponding data information in the 
                           the follwing tabs",choices=unique(midterm$id)),
               tableOutput("studentouptput")
               
  ),

  mainPanel(
    tabsetPanel(
      
      tabPanel("General",
               h4("About the quiz question items"),
               actionButton("topic_cover","Topic_Coverage"),
               actionButton("topic_dist","Topic_Distribution"),
               actionButton("item_diff","Item_difficulty"),
               plotlyOutput("topic"),
               plotlyOutput("topic2"),
               plotlyOutput("itdiff")
               ),
    
      tabPanel("Individual Diagonistic",
               h4("Individual's test monitoring"),
               plotlyOutput("student1"),
               plotlyOutput("student2"),
               plotlyOutput("mastery")
               ),
    
      tabPanel("Time v.s Clickcount v.s Correct Rate",
               h4("Exploring Relationship"),
               selectInput("x","X-axis",choices = c("Time","Outcome.y","Click")),
               selectInput("y","Y-axis",choices = c("Click","Outcome.y","Time")),
               selectInput("col","Color",choices = c("Outcome.y","Time","Click")),
               selectInput("size","Weighted Point Size",choices = c("Click","Outcome.y","Time")),
               plotlyOutput("relation")
               )
  )
  )
)
)


server <- function(input, output) {
  
  output$studentouptput<-renderTable({
    filter(midterm[,c(1,89:91)],id==input$studentid)
  })
  
  #Activation by a button
  observeEvent(input$item_diff,
  output$itdiff<-renderPlotly({
  plot1<-ggplot(item_diff,aes(x=Question,y=item_difficulty_rate))+
  geom_line(group=1)+
  geom_point(aes(col=item_difficulty),alpha=0.8)+
  theme(rect=element_blank(),
        line=element_blank())+
  labs(title = "Distribution of Question items with Different Difficulty")
  
  ggplotly(plot1)
  }))
  
  observeEvent(input$topic_cover,
  output$topic <- renderPlotly({
  plot1<-ggplot(quiz_reshape1,aes(x=Question,fill=categories))+
  geom_bar()+
  coord_flip()+ylim(c(0,5))+
  ylab("Topics and Number")+
  xlab("Question Item")+
  theme(rect=element_blank(),
        line=element_blank())+
  labs(title = "What is/are Tested in each Question")+
  scale_fill_manual(values = mycolors)
  
  ggplotly(plot1)
  }))
  
  observeEvent(input$topic_dist,
  output$topic2 <- renderPlotly({
  plot1<-ggplot(quiz_reshape1,aes(x=categories,fill=categories))+
        geom_bar()+ylim(c(0,25))+
        theme(rect=element_blank(),
              line=element_blank(),
              axis.text.x = element_text(angle=90))+
              xlab("Topics")+
    labs(title = "Distribution of Topics")+
    theme(axis.text.x  = element_text(angle=45, hjust = 1))+scale_fill_manual(values = mycolors)
  ggplotly(plot1)
  }))
  
  output$student1<-renderPlotly({
 
    test1<-subset(a,id==input$studentid)
    
    p1<-ggplot(test1,aes(x=Question,y=Time))+
      geom_point(aes(col=Outcome))+geom_line(group = 1)+
      theme(rect=element_blank())+
      ylim(c(0,800))+
      labs(title = "Time You Spent on each Question")

     # grid.newpage()
     # grid.draw(rbind(ggplotGrob(ggplotly(p1)), ggplotGrob(ggplotly(p2)), size ="last") )  
     ggplotly(p1)
  })
  
  
  output$student2<-renderPlotly({
 
    test2<-subset(a1,id==input$studentid)  

   p2<-ggplot(test2,aes(x=Question,y=Click))+
     geom_col(aes(fill=Outcome))+
     theme(rect=element_blank())+
     labs(title = "Times You Click on each Question")

     ggplotly(p2)
  })
  
  
  
    
  output$mastery<-renderPlotly({
    test<-subset(midterm_long,id==input$studentid)
    plot1<-ggplot(test,aes(x=categories,fill=Outcome))+
      geom_bar(position = "fill",width = 0.6)+
      theme(rect=element_blank(),
            line=element_blank(),
            axis.text.x = element_text(angle=90))+
      xlab("Categories")+
      ylab("Proportion of Correct Answers")+
      labs(title = "How You Master each of the Topics")+
      theme(axis.text.x  = element_text(angle=45, hjust = 1))
    ggplotly(plot1)
  })
  

  plot1<-reactive({ggplot(data=relation, aes_string(x=input$x,y=input$y,col=input$col,size=input$size))+
        geom_point(alpha=0.8)+
        theme(rect=element_blank())
    
  })
  output$relation<-renderPlotly({
    ggplotly(plot1())
  })
  
}

shinyApp(ui = ui, server = server)
```